Survey.jl - An Efficient Framework for Analysing Complex Surveys

### 2024-05-27 paper/header.tex
Update header.tex
Added co-author
Update paper/header.tex
Co-authored-by: Nadia <76887318+nadiaenh@users.noreply.github.com>

@@

\hypersetup{
pdftitle = {Survey.jl - An Efficient Framework for Analysing Complex Surveys},
pdfsubject = {JuliaCon 2022 Proceedings},
pdfauthor = {Ayush Patnaik},
pdfkeywords = {Julia, Survey, Statistics, Sampling},
}

>>>>

\author[2]{Nadia Enhaili}
\affil[2]{Simon Fraser University}

@@

\hypersetup{
pdftitle = {Survey.jl - An Efficient Framework for Analysing Complex Surveys},
pdfsubject = {JuliaCon 2023 Proceedings},
pdfauthor = {Ayush Patnaik},
pdfkeywords = {Julia, Survey, Statistics, Sampling},
}
